Flatiron cleaning

### 2022-05-19 Rmd/Manuscript rdi analysis.Rmd
Update for carbo only analysis

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup()

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
```

@@

```{r RDI_data}
RDI_data <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, 
       RDI_pacli_neo, RDI_pacli_neo_grp, 
       RDI_carbo_adj, RDI_carbo_adj_grp, 
       RDI_pacli_adj, RDI_pacli_adj_grp, 
       .direction = "downup") %>% 
  ungroup()
Frontline_adjusted <- RDI_data %>% 
  distinct(patientid, .keep_all = TRUE)
```
<br>
<br>

# **Number of patients : `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**

@@

<!-- ```{r rule between diagnosis and treatment} -->
<!-- drugs1 <- Frontline_adjusted %>%  -->
<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
<!--   group_by(patientid) %>%  -->
<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
<!--            duration(n=1, units = "days") -->
<!--   ) -->
<!-- ``` -->

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- Frontline_adjusted %>% 
  filter(is.na(flatiron_rules))
```

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) # %>% 
  # filter(histology == "Serous")

@@

study_criteria <- study_criteria %>%
  filter(had_carbo_pacli == "Yes")

@@

- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
- exclude patients for whose no RDI were available

@@

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((
    therapy == "Upfront Chemo" &
      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
  ) | (
    therapy == "Upfront Surgery" &
      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
  )
  )
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

@@

  # anti_join is useful for counting exclusions -------------
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • (Data from one PracticeID) <br>
      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include only patients who received platin and/or taxane <br>
      • exclude patients who only received neo + surgery <br>
      • include patients with single or dual P/T +/- Bev as frontline treatment
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

@@

# II.Data analysis
## Explore the dataset

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

<!-- ### Number of line /cycle received by patients in our study population  -->

<!-- <span style="color:green">**Table supp X Number of total line**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   arrange(desc(linenumber_new)) %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linenumber_new, therapy) %>%  -->
<!--   tbl_summary(by = therapy) -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Neo**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>%  -->
<!--   tbl_summary() -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>%  -->
<!--   tbl_summary(type = list(cycle_increment ~ "continuous")) -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Adj**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>%  -->
<!--   tbl_summary(by = therapy) -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>%  -->
<!--   tbl_summary(by = therapy, -->
<!--               type = list(cycle_increment ~ "continuous")) -->
<!-- ``` -->
<!-- <br> -->

@@

# Clinical Analysis

## ICC between cycles
```{r}
full_data_study_pop

## 1.Clinical summary table

<span style="color:green">**Table X Overall summary demographic/clinical data**</span>
```{r Table 1}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

@@

<span style="color:green">**Table X Summary demographic/clinical data by race**</span>
```{r Table 2}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

@@

## <span style="color:green">**Table 1 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",
            histology1, "histology",
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat,
           therapy, debulking, imp_debulking)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

<span style="color:green">**Table X Summary treatment data by race**</span>
```{r Table 4}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", imp_debulking , "therapy"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

<span style="color:green">**Table X Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,
           "debulking", imp_debulking, "therapy"
           )) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```

## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span>
Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, dose received, 
         RDI per patient/therapy/settings for each drug name.  
The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj).
```{r Summary of the expected, actual dose, and RDI}
tbl <- full_data_study_pop %>% 
  group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
  summarise(amount = mean(amount), 
            BSA = mean(BSA), 
            height = mean(height), 
            weight = mean(weight), 
            creatinine = mean(creatinine),
            CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose),
            relative_dose_intensity = mean(mean_RDI_per_drug)) %>% 
  ungroup() %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant")))

@@

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
        imp_stagecat#) 
      + #strata(
        histology#) 
      + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
        imp_stagecat + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()

@@

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology)
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

>>>>

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(irr)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
```

@@

```{r RDI_data}
RDI_data <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, 
       RDI_pacli_neo, RDI_pacli_neo_grp, 
       RDI_carbo_adj, RDI_carbo_adj_grp, 
       RDI_pacli_adj, RDI_pacli_adj_grp, 
       .direction = "downup") %>% 
  ungroup()
RDI_data_per_patients <- RDI_data %>% 
  mutate(carbo_arrange_variable = case_when(
    drugname == "carboplatin"           ~ 1
  )) %>% 
  arrange(carbo_arrange_variable) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(-c(linename, linenumber, linenumber_adj, 
            linenumber_new, linestartdate, lineenddate,
            cycle_drugname, cycle_increment, cycle_start_date,
            cycle_count_perline, cycle_major_drugname))
```
<br>
<br>

# **Number of patients : `r RDI_data_per_patients %>% distinct(patientid) %>% nrow()`**

@@

<!-- ```{r rule between diagnosis and treatment} -->
<!-- drugs1 <- RDI_data_per_patients %>%  -->
<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
<!--   group_by(patientid) %>%  -->
<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
<!--            duration(n=1, units = "days") -->
<!--   ) -->
<!-- ``` -->

@@

Are excluded :  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- RDI_data_per_patients %>% 
  filter(is.na(flatiron_rules))
```

@@

-	exclude borderline cases (not invasive ovarian cancer)  
- exclude patients whose histology is unknown  
- remove chemotherapy only patients  
- include only patients who received platin and/or taxane (exclude patients who didn't received carboplatin)  
- exclude patients who only received neo + surgery  
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(is.na(borderline))

study_criteria <- study_criteria %>% 
  filter(!is.na(histology)) # %>% 
  # filter(histology == "Serous") 
  # filter(histology == "Others")

@@

study_criteria <- study_criteria %>%
  filter(had_carbo == "Yes")

@@

- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
- exclude patients for whose no RDI were available FOR CARBOPLATIN

@@

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((
    therapy == "Upfront Chemo" &
      (!is.na(RDI_carbo_neo) & 
         !is.na(RDI_carbo_adj)) 
  ) | (
    therapy == "Upfront Surgery" &
      (!is.na(RDI_carbo_adj))
  )
  )
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  RDI_data_per_patients %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(is.na(borderline)) %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

@@

  # anti_join is useful for counting exclusions
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • **(Data from one PracticeID)** <br>
      • **(historical structured data were not available for <br> patients seen at academic sites prior to 2015)**
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • Borderline cases (not invasive ovarian cancer) <br>
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

@@

# II.Data analysis
## Explore the dataset
## <span style="color:green">**ICC between cycles**</span>

Used the ICC for a single rater, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for both test-retest and intra-rater reliability studies (Koo et al., 2016).  
<!-- **For ICC, a value of 0.9 is considered as excellent.**  -->
```{r}
# Need to recalculate the average per cycle as we did it by line (was comaing back to same because we limit our study to 1+1 or 1+3 cycle type)
# What I did :
# Treatment <- Treatment %>% 
#   mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
#   ) %>%
#   group_by(patientid, chemotherapy_type, drugname) %>%
#   mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
#   ) %>% 
#   ungroup()

Treatment_ICC <- 
  Treatment %>% 
  # Limit to the patietns after exclusion criteria
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  filter(linenumber_adj == 1) %>% 
  filter(had_carbo == "Yes") %>% 
  arrange(patientid, episodedate) %>% 
  # group to have RDI by cycle for each drug 
  group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
  mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>%
  arrange(patientid, episodedate) %>% 
  distinct(patientid, chemotherapy_type, cycle_increment, drugname, .keep_all = TRUE) %>% 
  filter(drugname == "carboplatin")
```

```{r}
ICC_df <- Treatment_ICC %>% select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
  unite(patientid, c(patientid:chemotherapy_type)) %>%
      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
      select(-patientid)

icc_value <- round(icc(
      ICC_df, model = "twoway", 
      type = "agreement", unit = "single"
    )$value, 3)
head(ICC_df, 10)

# mutate(reliability = case_when(
#   value < 0.5 ~ "poor",
#   value >= 0.5 &
#     value < 0.75 ~ "moderate",
#   value >= 0.75 &
#     value < 0.9 ~ "good",
#   value >= 0.9 ~ "excellent"
# ))
```
The ICC value is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`

```{r}
full_data_study_pop <-
  Treatment %>%
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
  arrange(patientid, episodedate, drugname) %>% 
  filter(had_carbo == "Yes") %>% 
  filter(linenumber_adj == 1)
```

### Number of cycle received by patients in our study population

<!-- <span style="color:green">**Table supp X Number of total line**</span> -->
```{r}
# full_data_study_pop %>%
#   arrange(desc(linenumber_new)) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(linenumber_new, therapy) %>%
#   tbl_summary(by = therapy)
```

<span style="color:green">**Table supp X Number of cycle in Neo**</span>
```{r}
full_data_study_pop %>%
  filter(chemotherapy_type == "Neoadjuvant") %>%
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>%
  tbl_summary()
full_data_study_pop %>%
  filter(chemotherapy_type == "Neoadjuvant") %>%
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>%
  tbl_summary(type = list(cycle_increment ~ "continuous"))

full_data_study_pop %>%
  filter(chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linename) %>%
  tbl_summary()
```

<span style="color:green">**Table supp X Number of cycle in Adj**</span>
```{r}
full_data_study_pop %>%
  filter(chemotherapy_type == "Adjuvant") %>%
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, therapy) %>%
  tbl_summary(by = therapy)
full_data_study_pop %>%
  filter(chemotherapy_type == "Adjuvant") %>%
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, therapy) %>%
  tbl_summary(by = therapy,
              type = list(cycle_increment ~ "continuous"))

full_data_study_pop %>%
  filter(chemotherapy_type == "Adjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linename, therapy) %>%
  tbl_summary(by = therapy)
```
<!-- <br> -->

@@

# Clinical Analysis
## 1.Clinical summary table

<span style="color:green">**Table X Overall summary demographic/clinical data**</span>
```{r Table 1}
Frontline %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

@@

<span style="color:green">**Table X Summary demographic/clinical data by race**</span>
```{r Table 2}
Frontline %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

@@

## <span style="color:green">**Table 1 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",
            histology1, "histology",
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat,
           therapy, debulking, imp_debulking)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

<span style="color:green">**Table X Summary treatment data by race**</span>
```{r Table 4}
Frontline %>% 
  select(c(raceeth,
           "debulking", imp_debulking , "therapy"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

<span style="color:green">**Table X Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% 
  select(c(bmi_cat,
           "debulking", imp_debulking, "therapy"
           )) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```

## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span>
Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, dose received, 
         RDI per patient/therapy/settings for each drug name.  
The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj).
```{r Summary of the expected, actual dose, and RDI}
tbl <- 
  Treatment %>% 
  # Limit to the patietns after exclusion criteria
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname) %>% 
  # group to have RDI by cycle for each drug 
  # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
  # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # ) %>% 
  # ungroup() %>% 
  filter(drugname == "carboplatin") %>% 
  filter(linenumber_adj == 1) %>%

  group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
  summarise(amount = mean(amount), 
            BSA = mean(BSA), 
            height = mean(height), 
            weight = mean(weight), 
            creatinine = mean(creatinine),
            CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose),
            relative_dose_intensity = mean(mean_RDI_per_drug)) %>% 
  ungroup() %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant")))

@@

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        imp_stagecat + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()

@@

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology),
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
